\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{enumitem}



% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[SACMAT'17]{ACM SACMAT conference}{July 2017}{Indianapolis, Indiana USA} 
%\acmYear{2017}
%\copyrightyear{2017}
%
%\acmPrice{15.00}


\begin{document}
%\title{Device Anomaly detection using Provenance Graphs}
\title{  Anomaly Detection in IoT Devices using Provenance Graphs}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Ebelechukwu Nwafor}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Howard University}
% \streetaddress{P.O. Box 1212}
  \city{Washington} 
  \state{DC} 
  \postcode{20059}
}
\email{ebelechukwu.nwafor@bison.howard.edu}

\author{Gedare Bloom}
%\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Howard University}
%  \streetaddress{P.O. Box 1212}
  \city{Washington} 
  \state{DC} 
  \postcode{20059}
}
\email{gbloom@howard.edu}

%\author{Lars Th{\o}rv{\"a}ld}
%\authornote{This author is the
%  one who did all the really hard work.}
%\affiliation{%
%  \institution{The Th{\o}rv{\"a}ld Group}
%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%  \city{Hekla} 
%  \country{Iceland}}
%\email{larst@affiliation.org}
%
%\author{Lawrence P. Leipuner}
%\affiliation{
%  \institution{Brookhaven Laboratories}
%  \streetaddress{P.O. Box 5000}}
%\email{lleipuner@researchlabs.org}
%
%\author{Sean Fogarty}
%\affiliation{%
%  \institution{NASA Ames Research Center}
%  \city{Moffett Field}
%  \state{California} 
%  \postcode{94035}}
%\email{fogartys@amesres.org}
%
%\author{Charles Palmer}
%\affiliation{%
%  \institution{Palmer Research Laboratories}
%  \streetaddress{8600 Datapoint Drive}
%  \city{San Antonio}
%  \state{Texas} 
%  \postcode{78229}}
%\email{cpalmer@prl.com}
%
%\author{John Smith}
%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
%\email{jsmith@affiliation.org}
%
%\author{Julius P.~Kumquat}
%\affiliation{\institution{The Kumquat Consortium}}
%\email{jpkumquat@consortium.net}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}

The Internet of Things (IoT) has revolutionized the way we interact with devices. From smart grids, to healthcare and home automation systems. This paradigm shift inadvertently allows for ease of device access. Unfortunately, this technological advancement has been met with unforeseen security challenges. One major challenge is malicious intrusions --A common way of detecting a malicious attack is by treating an attack as an  anomaly and using anomaly detection techniques to pinpoint the source of an intrusion. In a given IoT device, provenance graphs which denotes causality  between system events offers immense benefit for anomaly detection. Provenance provides a comprehensive history of activities performed on a system which indirectly ensures trust. Given a provenance graph, how do we determine if anomalous activities exists? This paper seeks to address this issue. In this paper, We introduce an error tolerant graph embedding technique using frequencies of nodes and edges in which provenance graphs are converted into a vector space representation. This vector space representation of the graphs from learning and detection phase is used as an input  parameter to our anomaly detection algorithm. we propose two anomaly detection algorithms using provenance graphs. The first approach involves the use of a similarity metric to compare provenance graphs while the later involves the use of a hybrid anomaly detection algorithm. We evaluate the effectiveness of our approach with IoT applications which generates provenance graphs.

%We compare our method to two known anomaly detection algorithms. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 




\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Information Science ~Data Provenance</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Computer Applications ~Access Control</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Internet of Things}
\ccsdesc{Computer systems organization~Data Provenance}
 

% We no longer use \terms command
%\terms{Theory}

\keywords{IoT, Data Provenance, Anomaly Detection}


\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{anomaly_detection} 

\end{document}
